An Abstraction-based Approach to Network Synthesis

### 2016-11-03 paper/abstraction/paper.tex
add analysis image

The idea is to maintain, for each role in the abstract product graph, facts learned about the number of disjoint paths to some number of concrete routers in that role from a given source location. More specifically, we maintain facts of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k) 
\end{array} \]
\noindent
%
Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all". There is one label in the nesting for each pod scope in the network abstraction hierarchy. So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label. The value $j$ tells us the number of concrete nodes in the group that are reachable, and the value $k$ tells us the number of disjoint paths to each of the $j$ nodes such that all $j*k$ paths are disjoint.

>>>>

The idea is to maintain, for each role in the abstract product graph, facts learned about the number of disjoint paths to some number of concrete routers in that role from a given source location. More specifically, we maintain facts of the form:
%
\[ \begin{array}{c}
  L_{X_1}, \ldots, L_{X_n}(j,k) 
\end{array} \]
\noindent
%
Each label $L \in \{S,A\}$ is either $S$, which stands for ``some" or is $A$, which stands for ``all". There is one label in the nesting for each pod scope in the network abstraction hierarchy. So for a given node, $L_{X_1}$ would correspond to the outermost pod scope, while $L_{X_n}$ would correspond the the node's label.

Semantically, $L_{X_1}, \ldots, L_{X_n}(j,k)$ means that starting from some concrete router in the abstract source, for ``some"/``all" scopes $X_1$, $L_{X_2}, \ldots, L_{X_n}(j,k)$ holds. The base case $L_{X_n}(j,k)$ means that for ``some"/``all" groups of size $j$ concrete routers, there are $k$ disjoint paths to each such that all $j*k$ paths are disjoint

\begin{figure}
  \begin{center}
    \includegraphics[width=.66\columnwidth]{figures/analysis}
  \end{center}
  \caption{Abstract disjoint path analysis with valleyfree routing for global prefixes. \label{fig:compilation-times}}
  \vspace{-1em}
\end{figure}

For example, a fact of the form: $A_P, S_{TL}(2,4)$ means that for all pods P, there is some group of size 2 concrete routers in role TL such that they each have 4 disjoint to them from the source and all 8 paths are disjoint.

%suppose we want to compute the number of disjoint paths from the local ToR role $(TL,0,0)$ for  
\ryan{TODO: probably need a new image for local prefixes?}
